A template for the \emph{arxiv} style

### 2021-08-08 main/main.Rmd
add description of each section, a new section on to introduce manipulation/ vis with cubble

Spatio-temporal data

@@

Motivation: Many focus on spatio/ temporal solely -> spatio-temporal vector data structure for data analysis

sections

@@

>>>>

Saptio-temporal data

<!-- Spatio-temporal data requires the data to have both a time aspect that is long enough to be considered as time series data and a space aspect that spreads across the a certain geographical region. In the time aspect, we may expect to see trend and seasonality across different granularities and in the spatio aspect, similarity of patterns can be discovered. -->

<!-- can see information of both dimension,  -->
<!-- not sufficient implementation to manipulate and visualise spatio-temporal data. more focus solely on the spatio/ temporal aspect.  -->
<!-- The purpose of this paper is to introduce a spatio-temporal vector data structure for data analysis in R -->

@@

The rest of the paper will be divided as follows: Section 2 reviews the existing data structure for spatio, temporal, and spatio-temporal data. Section 3 presents a new data structure for spatio-temporal data: cubble. Then the paper introduces the workflow of data manipulation and visualisation with the cubble structure in Section 4. Section 5 gives some examples on how common spatial and temporal manipulations are performed with cubble and how static and interactive visualisation help ot understand climate and [...] data.

@@

# Manipulation and visualisation with `cubble`

Mention different types of manipulation with cubble:

  - `dplyr` support for cubble: 
    - basic 5s: mutate, filter, summarise, select, arrange
    - group and ungorup: group_by, ungroup
    - slice family
  - summarise missing stats

### 2021-08-08 main/main.tex
add description of each section, a new section on to introduce manipulation/ vis with cubble

Spatio-temporal data

Motivation: Many focus on spatio/ temporal solely -\textgreater{}
spatio-temporal vector data structure for data analysis

sections

@@

>>>>

Saptio-temporal data

The rest of the paper will be divided as follows: Section 2 reviews the
existing data structure for spatio, temporal, and spatio-temporal data.
Section 3 presents a new data structure for spatio-temporal data:
cubble. Then the paper introduces the workflow of data manipulation and
visualisation with the cubble structure in Section 4. Section 5 gives
some examples on how common spatial and temporal manipulations are
performed with cubble and how static and interactive visualisation help
ot understand climate and {[}\ldots{]} data.

@@

\hypertarget{manipulation-and-visualisation-with-cubble}{%
\section{\texorpdfstring{Manipulation and visualisation with
\texttt{cubble}}{Manipulation and visualisation with cubble}}\label{manipulation-and-visualisation-with-cubble}}

Mention different types of manipulation with cubble:

\begin{itemize}
\tightlist
\item
  \texttt{dplyr} support for cubble:

  \begin{itemize}
  \tightlist
  \item
    basic 5s: mutate, filter, summarise, select, arrange
  \item
    group and ungorup: group\_by, ungroup
  \item
    slice family
  \end{itemize}
\item
  summarise missing stats
\end{itemize}
